Notes of Basic Topolgy

### 2016-12-01 Basic Topology Notes/sections/ch5-fundamental-groups.tex
New Basic Topology Notes: about triangulation technique.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.7\linewidth]{pics/homotopy-for-loops-2.PNG}
    \caption{Homotopy for loops 2 (pp. 88 of \cite{book})}
\end{figure}
\begin{ex}
    The author shows on page 88 of \cite{book} that: when $C$ is a
    convex subset of a euclidean space, let $f,g:X\to C$ be continuous
    maps, then $f\simeq_F g$, where $F$ is $F(x,t)=(1-t)f(x)+tg(x)$.
    Note that if $f$ and $g$ agree on a subset $A$ of $X$, then this
    homotopy is a homotopy relative to $A$. This $F$ is called a
    \nomen{straight-line homotopy}.
\end{ex}
\begin{ex}
    Let $f,g:X\to S^n$ be continuous maps. We can take $S^n$ to be the
    unit sphere in $\mathbb{E}^{n+1}$, and think of $f,g$ as
    continuous maps into $\mathbb{E}^{n+1}$, then we may form a
    straight-line homotopy from $f$ to $g$ by:
    \begin{equation}
        F(x,t) = \frac{(1-t)f(x)+tg(x)}{||(1-t)f(x)+tg(x)||}
    \end{equation}
    Notice that the ball $B^{n+1}$ is a convex set, so the numerator
    lies inside the ball. When normalized (as in $F(x,t)$), the
    numerator is a point on the sphere.
\end{ex}
\begin{ex}
    This is example is best illustrated by pictures:
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/{loops-to-loops-fig5.2}.PNG}
        \caption{Loops to loops (pp. 89 of \cite{book})}
    \end{figure}
    Geometrieally, $\alpha$ winds eaeh of the segments
    $[O,\frac{1}{2}]$, $[\frac{1}{2},\frac{3}{4}]$, $[\frac{3}{4}, 1]$
    once round the eirc1e, the first two being wound in an
    anticlockwise direetion, and the third clockwise. The loop $\beta$
    simply winds the whole interval $[0,1]$ once round the circle
    anticlockwise.

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.7\linewidth]{pics/homotopy-for-loops-2.PNG}
    \caption{Homotopy for loops 2 (pp. 88 of \cite{book})}
\end{figure}
\begin{ex}
    The author shows on page 88 of \cite{book} that: when $C$ is a
    convex subset of a euclidean space, let $f,g:X\to C$ be continuous
    maps, then $f\simeq_F g$, where $F$ is $F(x,t)=(1-t)f(x)+tg(x)$.
    Note that if $f$ and $g$ agree on a subset $A$ of $X$, then this
    homotopy is a homotopy relative to $A$. This $F$ is called a
    \nomen{straight-line homotopy}.
\end{ex}
\begin{ex}
    Let $f,g:X\to S^n$ be continuous maps. We can take $S^n$ to be the
    unit sphere in $\mathbb{E}^{n+1}$, and think of $f,g$ as
    continuous maps into $\mathbb{E}^{n+1}$, then we may form a
    similar "straight-line homotopy" from $f$ to $g$ by:
    \begin{equation}
        F(x,t) = \frac{(1-t)f(x)+tg(x)}{||(1-t)f(x)+tg(x)||}
    \end{equation}
    Notice that the ball $B^{n+1}$ is a convex set, so the numerator
    lies inside the ball. When normalized (as in $F(x,t)$), the
    numerator is a point on the sphere.
\end{ex}
\begin{ex}
    This is example is best illustrated by pictures:
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/{loops-to-loops-fig5.2}.PNG}
        \caption{Loops to loops (pp. 89 of \cite{book})}
    \end{figure}
    Geometrieally, $\alpha$ winds eaeh of the segments
    $[O,\frac{1}{2}]$, $[\frac{1}{2},\frac{3}{4}]$, $[\frac{3}{4}, 1]$
    once round the eirc1e, the first two being wound in an
    anticlockwise direetion, and the third clockwise. The loop $\beta$
    simply winds the whole interval $[0,1]$ once round the circle
    anticlockwise.
